\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-10-25 paper/mswp2012-proposal.tex
first version of Proposal (in German)

\note{
\begin{itemize}
	\item {\em Length: 1-2 pages}
	\item Concise presentation of the scientific proposal, with particular attention to the ground-breaking nature of the research project, which will allow to assess the feasibility of the outlined scientific approach. 
	\item WHY would you like to do WHAT, HOW would you like to do it and what are the expected RESULTS?
	\item Short description of project idea.
	\item Short description of problem / situation.
	\item What makes it an interesting endeavor?
	\item Why should somebody care?
	\item Very short cost-benefit description (what are potential benefits that make them worth the costs of the project?).
	\item Who are the beneficiaries of the results?
	\item Problem classification (to which scientific area does the project belong?; is it basic or applied research?)
	\item Constraints
	\begin{itemize}
		\item     The project must have an extent that demands to handle it as a project including project organization.  (No 2 person pieces; no 150 person-year efforts)
		\item     Software development should be part of the project. (But not its only content or scientific contribution.)
		\item     The project should be interesting and meaningful.
		\item     {\em Your creativity is called for!!}
	\end{itemize}
\end{itemize}
}

>>>>

% \note{
%\begin{itemize}
%	\item {\em Length: 1-2 pages}
%	\item Concise presentation of the scientific proposal, with particular attention to the ground-breaking nature of the research project, which will allow to assess the feasibility of the outlined scientific approach. 
%	\item WHY would you like to do WHAT, HOW would you like to do it and what are the expected RESULTS?
%	\item Short description of project idea.
%	\item Short description of problem / situation.
%	\item What makes it an interesting endeavor?
%	\item Why should somebody care?
%	\item Very short cost-benefit description (what are potential benefits that make them worth the costs of the project?).
%	\item Who are the beneficiaries of the results?
%	\item Problem classification (to which scientific area does the project belong?; is it basic or applied research?)
%	\item Constraints
%	\begin{itemize}
%		\item     The project must have an extent that demands to handle it as a project including project organization.  (No 2 person pieces; no 150 person-year efforts)
%		\item     Software development should be part of the project. (But not its only content or scientific contribution.)
%		\item     The project should be interesting and meaningful.
%		\item     {\em Your creativity is called for!!}
%	\end{itemize}
%\end{itemize}
%}

Das Projekt verfolgt das Ziel eine Plattform im Bereich e-Health zu schaffen. Diese Platform soll für die Nutzer ein Bonus-System bereitstellen und die Möglichkeit bieten herauszufinden, wie gesund die einzelnen Nutzer leben.\\

Das Projekt wird hierbei in verschiedene Phasen aufgeteilt, die eine langfristige Weiterentwicklung möglich machen bzw. mögliche Ausbaustufen aufzeigen. Für jeden der Phasen müssen Vertragspartner gefunden werden, die sich an der Plattform beteiligen. Diese Vertragspartner versorgen die Nutzer mit Boni und bekommen als Benefit eine Steigerung der Kundenbindung bzw. eine Möglichkeit Werbepräsenz auf der Plattform zu ergattern.\\

Mögliche Vertragspartner sind:
\begin{itemize}
	\item Phase 1:
		\begin{itemize}
			\item Supermärkte
			\item Fitness-Center
			\item Restaurants
		\end{itemize}
	\item Phase 2 - \"Einbindung bestehender Services\":
		\begin{itemize}
			\item Laufplattformen mit Tracking (Runtastic, RunKeeper, etc.)
			\item andere Sporttracking-Services (Schrittzähler, etc.)
		\end{itemize}
	\item Phase 3 - \"Health Organisations\":
		\begin{itemize}
			\item Versicherungsunternehmen
		\end{itemize}
\end{itemize}

Die Nutzer haben die Möglichkeit beim Einkauf oder Konsumation bei einem der Vertragspartner selbiges über eine App registrieren lassen. Im System werden dann anonymisiert die Einkäufe in Kategorien gespeichert und nach einem vorgefertigtem transparenten Punkteschmea bewertet.\\

Die Punkte können nach einer bestimmten Zeitspanne durch Gutscheine eingelöst werden, die dann bei den Vertragspartnern wieder eingelöst werden können. Ebenso können über die Plattformen Rankings und Verlosungen vorgenommen werden. Die Vertragspartner können die Nutzer über die App über neue Aktionen informieren, über die Zusatzpunkte erworben werden können.
